No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System

### 2019-04-24 apj_v2/ms.tex
revisions

\documentclass[twocolumn]{aastex62}

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}. Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit and a possible transit timing variation \citep[][ hereafter TK18]{teachey18b}. The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.

Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method. Motivated by this result, in this work we perform an independent reduction and fit to the HST light curve.

@@

@@

\section{Analysis}
The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signals and instrument systematic noise, which we model simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}. %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the planet's time of central transit, the planet inclination, and the planet mass. For the moon model, we added a third body with six free parameters: moon radius, moon time of central transit, moon orbital period, moon inclination, moon mass, and longitude of the ascending node relative to that of the planet.  We fixed the eccentricity of all bodies to zero. We also fixed the planet's orbital period to 287.378949 days (the best fit from TK18).

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$. The moon inclination was uniform from $89.7 - 90^\circ$ (to exclude grazing moon transit scenarios, where the moon radius could be arbitrarily large). The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 180^\circ$.

@@

We estimated the host star parameters using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}. We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters. The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr. In our analysis, we fixed the stellar mass to the best fit value ($1.37\,M_\odot$), and used a Gaussian prior on the radius, $R_* \sim N(1.81, 0.17)$.

@@

We obtained a slightly lower rms with the moon model (351 ppm); however, this is not a large enough improvement in fit quality to merit the addition of six additional free parameters.  The moon model has a small increase in $\chi^2_\nu$ to 1.02. According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 26.7$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time is not unimodal, and the $2\,\sigma$ confidence interval for the moon's transit spans the entire duration of the observations.  The upper limit on the moon radius is $3.5\,R_\oplus$ at $3\sigma$ confidence.

@@

@@

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.

The mid-transit times from the two fits agree better. TK18 found that the planet transited earlier than expected based on the Kepler data. Our posterior distribution for the planet's transit time agrees with TK18 to within $1\sigma$, leaving open the possibility for transit timing variations due to another body in the system.

@@

There are a few other steps in the TK18 data reduction that would require substantial modification of our pipeline to recreate, but seem unlikely to be responsible for the difference. One of these is outlier masking. TK18 identify outliers with a Gaussian process fit to the pixel-level light curves, compared to our optimal extraction approach. Despite the difference, both methods flag $\sim$0.01\% of pixels as bad.  We also do not use the STScI software \texttt{aXeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.

We conclude that no single choice in the data reduction provides an easy explanation for the difference in our light curves. This finding illustrates the challenge of pushing measurement precision to the 100 ppm level, and highlights the importance of developing multiple independent pipelines to confirm cutting-edge results.

@@

\acknowledgments
We thank A. Teachey for helpful discussions and for providing the extracted light curve from TK18.  The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  
%We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

>>>>

\documentclass[twocolumn,trackchanges]{aastex62}

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.  \added{The first evidence for the exomoon candidate, Kepler-1625b I, was based on observations from \Kepler. The light curve showed drops in stellar flux that were attributed to a transiting exomoon; however, later analysis called this result into question, showing that the moon transit features were highly sensitive to the \Kepler\ reduction pipeline and the algorithm used to detrend the data \citep{teachey18b, rodenbeck18}.

Subsequent follow-up observations with \HST\ revived the possibility of an exomoon in the system based on two factors: a small drop in the system flux after the planet's transit egress and a transit timing variation \citep[][ hereafter TK18]{teachey18b}. The best fit moon had a large radius (comparable to that of Neptune), and if real, is unlike any moon in the Solar System.

Since the primary evidence for the exomoon now rests on the \HST\ transit light curve, in this work we perform an independent reduction and fit to the \HST\ data and compare it to the results from TK18.}

@@

\added{The broadband light curve is shown in Figure\,\ref{fig:raw}, in comparison to the light curve from TK18. We note that there are differences between the two data sets, particularly a kink near the moon-like transit feature identified by TK18.}

@@

\section{Analysis}
The extracted transit light transit light curve contains both astrophysical signals and instrument systematic noise, which we model simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}, \added{which calculates the three-dimensional motion of the star, planet, and moon over time under the influence of gravity}. %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the planet's time of central transit, the planet inclination, and the planet mass. For the moon model, we added a third body with six free parameters: moon radius, moon time of central transit, moon orbital period, moon inclination, moon mass, and longitude of the ascending node relative to that of the planet.  We fixed the eccentricity of all bodies to zero. We also fixed the  orbital period \added{of the planet-moon barycenter} to 287.378949 days (the best fit from TK18). \added{We elected not to vary the period of the planet-moon barycenter because it is poorly constrained from a single transit observation. A longer period would cause a longer transit duration for the planet, but this could equivalently result from a smaller impact parameter, a larger star, or a massive moon that significantly perturbs the planetary orbit.}

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.  The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 360^\circ$.  \added{The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet. A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet. We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit. We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.}

@@

We estimatea the host star parameters using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}. We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters. The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr. In our analysis, we fixed the stellar mass to the best fit value ($1.37\,M_\odot$), and used a Gaussian prior on the radius, $R_* \sim N(1.81, 0.17)$.

@@

We obtained a slightly lower rms with the moon model (351 ppm); however, this is not a large enough improvement in fit quality to merit the addition of six additional free parameters.  The moon model has a small increase in $\chi^2_\nu$ to 1.02. According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 26.7$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time spans the entire duration of the observations ($2\sigma$ confidence).  The upper limit on the moon radius is \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence.

@@

\added{The posterior probabilites for the planet's mass and radius are consistent with either a gas giant planet or brown dwarf. The radius is $11.1^{+0.5}_{-0.2}\,R_\oplus$ and mass is $10^{2.2\pm0.5}\, M_\oplus$.}

@@

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at \deleted{$r_\mathrm{moon} = 3.9\pm0.5\,R_\oplus$} \added{$r_\mathrm{moon} = 4.3\pm0.5\,R_\oplus$}  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence, and the transit time is unconstrained.

\added{Although the two data sets yield different constraints on the moon properties, the planet's mid-transit time agrees to better than $1\sigma$ for the two fits. The transit time is earlier than expected based on the Kepler data ($3\sigma$ confidence; TK18), suggesting that there are transit timing variations in the system. Such variation could arise from the presence of a moon, as suggested by TK18; however, the variation could also be caused by another planet in the system.}

@@

There are a few other steps in the TK18 data reduction that would require substantial modification of our pipeline to recreate, but seem unlikely to be responsible for the difference. One of these is outlier masking. TK18 identify outliers with a Gaussian process fit to the pixel-level light curves, compared to our optimal extraction approach. Despite the difference, both methods flag $\sim$0.01\% of pixels as bad.  We also do not use the STScI software \texttt{aXeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.  We conclude that no single choice in the data reduction provides an easy explanation for the difference in our light curves.

\added{During the referee process for this work, we learned of another manuscript that also reanalyzed the \HST\ transit observation \citep{heller19}. The best fit favored a moon model similar to that found by TK18;  however, an MCMC analysis did not converge on this model, leading the authors to conclude that the highest likelihood solution may be an outlier.}

Taken together, these findings illustrate the challenge of pushing measurement precision to the 100 ppm level, and highlight the importance of developing multiple independent pipelines to confirm cutting-edge results.

@@

\acknowledgments
We thank A. Teachey for helpful discussions and for providing the extracted light curve from TK18.  We also thank the anonymous referee for a thoughtful report that improved the manuscript. The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  
%We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

### 2019-04-24 arxiv_v1/ms.tex
revisions

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.  \added{The first evidence for the exomoon candidate, Kepler-1625b I, was based on observations from \Kepler. The light curve showed drops in stellar flux that were attributed to a transiting exomoon; however, later analysis called this result into question, showing that the moon transit features were highly sensitive to the \Kepler\ reduction pipeline and the algorithm used to detrend the data \citep{teachey18b, rodenbeck18}.

@@

Since the primary evidence for the exomoon now rests on the \HST\ transit light curve, in this work we perform an independent reduction and fit to the \HST\ data and compare it to the results from TK18.}

@@

\added{The broadband light curve is shown in Figure\,\ref{fig:raw}, in comparison to the light curve from TK18. We note that there are differences between the two data sets, particularly a kink near the moon-like transit feature identified by TK18.}

@@

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}, \added{which calculates the three-dimensional motion of the star, planet, and moon over time under the influence of gravity}. %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the planet's time of central transit, the planet inclination, and the planet mass. For the moon model, we added a third body with six free parameters: moon radius, moon time of central transit, moon orbital period, moon inclination, moon mass, and longitude of the ascending node relative to that of the planet.  We fixed the eccentricity of all bodies to zero. We also fixed the  orbital period \added{of the planet-moon barycenter} to 287.378949 days (the best fit from TK18). \added{We elected not to vary the period of the planet-moon barycenter because it is poorly constrained from a single transit observation. A longer period would cause a longer transit duration for the planet, but this could equivalently result from a smaller impact parameter, a larger star, or a massive moon that significantly perturbs the planetary orbit.}

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.  The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 360^\circ$.  \added{The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet. A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet. We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit. We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.}

@@

We obtained a slightly lower rms with the moon model (351 ppm); however, this is not a large enough improvement in fit quality to merit the addition of six additional free parameters.  The moon model has a small increase in $\chi^2_\nu$ to 1.02. According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 26.7$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time spans the entire duration of the observations ($2\sigma$ confidence).  The upper limit on the moon radius is \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence.

@@

\added{The posterior probabilites for the planet's mass and radius are consistent with either a gas giant planet or brown dwarf. The radius is $11.1^{+0.5}_{-0.2}\,R_\oplus$ and mass is $10^{2.2\pm0.5}\, M_\oplus$.}

@@

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at \deleted{$r_\mathrm{moon} = 3.9\pm0.5\,R_\oplus$} \added{$r_\mathrm{moon} = 4.3\pm0.5\,R_\oplus$}  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence, and the transit time is unconstrained.

\added{Although the two data sets yield different constraints on the moon properties, the planet's mid-transit time agrees to better than $1\sigma$ for the two fits. The transit time is earlier than expected based on the Kepler data ($3\sigma$ confidence; TK18), suggesting that there are transit timing variations in the system. Such variation could arise from the presence of a moon, as suggested by TK18; however, the variation could also be caused by another planet in the system.}

@@

\added{During the referee process for this work, we learned of another manuscript that also reanalyzed the \HST\ transit observation \citep{heller19}. The best fit favored a moon model similar to that found by TK18;  however, an MCMC analysis did not converge on this model, leading the authors to conclude that the highest likelihood solution may be an outlier.}

>>>>

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, was based on observations from \Kepler. The light curve showed drops in stellar flux that were attributed to a transiting exomoon; however, later analysis called this result into question, showing that the moon transit features were highly sensitive to the \Kepler\ reduction pipeline and the algorithm used to detrend the data \citep{teachey18b, rodenbeck18}.

@@

Since the primary evidence for the exomoon now rests on the \HST\ transit light curve, in this work we perform an independent reduction and fit to the \HST\ data and compare it to the results from TK18.

@@

The broadband light curve is shown in Figure\,\ref{fig:raw}, in comparison to the light curve from TK18. We note that there are differences between the two data sets, particularly a kink near the moon-like transit feature identified by TK18.

@@

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}, which calculates the three-dimensional motion of the star, planet, and moon over time under the influence of gravity. %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the planet's time of central transit, the planet inclination, and the planet mass. For the moon model, we added a third body with six free parameters: moon radius, moon time of central transit, moon orbital period, moon inclination, moon mass, and longitude of the ascending node relative to that of the planet.  We fixed the eccentricity of all bodies to zero. We also fixed the  orbital period of the planet-moon barycenter to 287.378949 days (the best fit from TK18). We elected not to vary the period of the planet-moon barycenter because it is poorly constrained from a single transit observation. A longer period would cause a longer transit duration for the planet, but this could equivalently result from a smaller impact parameter, a larger star, or a massive moon that significantly perturbs the planetary orbit.

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.  The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 360^\circ$.  The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet. A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet. We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit. We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.

@@

We obtained a slightly lower rms with the moon model (351 ppm); however, this is not a large enough improvement in fit quality to merit the addition of six additional free parameters.  The moon model has a small increase in $\chi^2_\nu$ to 1.02. According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 26.7$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time spans the entire duration of the observations ($2\sigma$ confidence).  The upper limit on the moon radius is $3.6\,R_\oplus$ at $3\sigma$ confidence.

@@

The posterior probabilites for the planet's mass and radius are consistent with either a gas giant planet or brown dwarf. The radius is $11.1^{+0.5}_{-0.2}\,R_\oplus$ and mass is $10^{2.2\pm0.5}\, M_\oplus$.

@@

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.3\pm0.5\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.6\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.

Although the two data sets yield different constraints on the moon properties, the planet's mid-transit time agrees to better than $1\sigma$ for the two fits. The transit time is earlier than expected based on the Kepler data ($3\sigma$ confidence; TK18), suggesting that there are transit timing variations in the system. Such variation could arise from the presence of a moon, as suggested by TK18; however, the variation could also be caused by another planet in the system.

@@

During the referee process for this work, we learned of another manuscript that also reanalyzed the \HST\ transit observation \citep{heller19}. The best fit favored a moon model similar to that found by TK18;  however, an MCMC analysis did not converge on this model, leading the authors to conclude that the highest likelihood solution may be an outlier.
